A Large-Area, Spatially Continuous Assessment of Land Cover Map Error and Its Impact on Downstream Analyses

### 2017-09-04 inst/paper/main.tex
Updated all vignettes so the rm(list = ls()) appeared above setting variable e (for running chunks all at once), which was causing some vignettes to fail at knit time. Rebuilt package.

\vspace{-0.5 cm}
\section*{Results}
\vspace{-0.3 cm}
\subsection*{Cropland map errors}
\vspace{-0.2 cm}
Our 1 km reference cropland map indicated that crop fields covered 104,304 km$^2$ (nearly 10\%) of the total study area in the 2009-2011 time period, with corresponding cropland area estimates of 131,390, 82,358, 77,090, and 110,272 (GeoWiki) km$^2$ resulting from the SA-LC, GlobCover, MODIS, and GLC-Share maps, respectively. Cropland area estimates from both the reference and test maps were constant for all levels of aggregation.

>>>>

\vspace{-0.5 cm}
\section*{Results}
\vspace{-0.3 cm}
\subsection*{Cropland map errors}
\vspace{-0.2 cm}
Our 1 km reference cropland map indicated that crop fields covered 104,304 km$^2$ (nearly 10\%) of the total study area in the 2009-2011 time period, with corresponding cropland area estimates of 131,390, 82,358, 77,090, and 110,272 km$^2$ resulting from the SA-LC, GlobCover, MODIS, and GLC-Share maps, respectively. Cropland area estimates from both the reference and test maps were constant for all levels of aggregation.
